Sound Automated Synthesis of Digital Controllers

### 2016-10-13 paper/paper.tex
Updated server CPU/RAM.

\textcolor{red}{Pascal: Can you please check whether this configuration is correct?}
All experiments were conducted on an otherwise idle Intel Core i$7$-$4790$ 
CPU $3$.$60$ GHz, $16$ GB of RAM, and Linux OS.  All times given are wall 
clock time in seconds as measured by the UNIX time command.

>>>>

All experiments were conducted on a 12-core 2.40\,GHz Intel Xeon E5-2440 with 96\,GB
of RAM, and Linux OS.  All times given are wall clock time in seconds as measured
by the UNIX date command.
